---
format: 
  html:
    toc: false
execute:
  eval: false
---

## How to install materials

To install the materials locally in your computer you have to follow these instructions:

<ol>
<li> Install the package {pak} (first time)

If you don't have this package, you have to install it for the first time:

```{r}
install.packages("pak")
```

<li> Install the package {CursBioR} (first time)

If you don't have the package, you have to install it for the first time:

```{r}
pak::pak("bruigtp/CursBioR")
```

</li>

<li> Load package and run `install_course()`

This function will save the materials to an existing path on your computer specified by the `destdir` argument:

```{r}
library(CursBioR)

#Download materials to your path:
install_course(destdir = "<YOUR_PATH>")
```

Remember that R can't read Windows backslash in paths (`\`). Thus, we have to manually change all the `\` for the `/` in a path:

 - Incorrect: `C:\Users\username\Documents\CursBioR`

 - Correct: `C:/Users/username/Documents/CursBioR`

::: {.callout-important}
The function downloads the material that has been posted up to that point. For each session, we have to repeat step 3 again to get the new material for the new sessions.
:::

</li>
</ol>